IRS-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design

### 2020-10-06 main.tex
:triangular_flag_on_post: Create backup

\begin{document}
	\title{IRS-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design}
	\author{
		\IEEEauthorblockN{
			Yang~Zhao,~\IEEEmembership{Student~Member,~IEEE,}
			Bruno~Clerckx,~\IEEEmembership{Fellow,~IEEE,}
			and~Zhenyuan~Feng,~\IEEEmembership{Student~Member,~IEEE}
		}
		\thanks{
			The authors are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (e-mail: yang.zhao18@imperial.ac.uk; b.clerckx@imperial.ac.uk).
		}
	}
	\maketitle

	\begin{abstract}
		The performance of Simultaneous Wireless Information and Power Transfer (SWIPT) is mainly restricted by the strength of the received Radio-Frequency (RF) signal. To tackle this problem, we introduce a low-power Intelligent Reflecting Surface (IRS) that compensates the propagation loss and boosts the energy efficiency with a passive beamforming gain. This paper investigates an IRS-aided Orthogonal Frequency Division Multiplexing (OFDM) SWIPT system based on a practical nonlinear energy harvester model, where a multi-antenna Access Point (AP) transmits information and energy simultaneously to a single-antenna user under the assist of IRS. We aim to maximize the Rate-Energy (R-E) region via jointly optimizing the transmit waveform at the AP, the reflection coefficients at the IRS, and the power splitting ratio at the user. The performance of the proposed waveform and beamforming design is compared with those of no IRS, fixed IRS and ideal frequency-selective (FS) IRS, and we confirm that due to rectifier nonlinearity, a dedicated power signal can be beneficial to energy harvesting (EH) while the optimal transceiving strategy depends on the system configuration. Simulation results also demonstrate that the proposed adaptive IRS design brings significant R-E enhancement over benchmark schemes for broadband transmission, and the optimal IRS can be approximated in closed form with negligible performance loss for SISO narrowband transmission.
	\end{abstract}

>>>>

\begin{document}
	\title{IRS-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design}
	\author{
		\IEEEauthorblockN{
			Yang~Zhao,~\IEEEmembership{Member,~IEEE}
			and~Bruno~Clerckx,~\IEEEmembership{Senior~Member,~IEEE}
		}
		\thanks{
			The authors are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (e-mail: yang.zhao18@imperial.ac.uk; b.clerckx@imperial.ac.uk).
		}
	}
	\maketitle

	\begin{abstract}
		The performance of Simultaneous Wireless Information and Power Transfer (SWIPT) is mainly restricted by the strength of the received Radio-Frequency (RF) signal. To tackle this problem, we introduce a low-power Intelligent Reflecting Surface (IRS) that compensates the propagation loss and boosts the energy efficiency with a passive beamforming gain. This paper investigates an IRS-aided Orthogonal Frequency Division Multiplexing (OFDM) SWIPT system based on a practical nonlinear energy harvester model, where a multi-antenna Access Point (AP) transmits information and energy simultaneously to a single-antenna user under the assist of IRS. We aim to maximize the Rate-Energy (R-E) region via jointly optimizing the transmit waveform at the AP, the reflection coefficients at the IRS, and the power splitting ratio at the user. The performance of the proposed waveform and beamforming design is compared with those of no IRS, fixed IRS and ideal frequency-selective (FS) IRS, and we confirm that due to rectifier nonlinearity, a dedicated power signal can be beneficial to energy harvesting (EH) while the optimal transceiving strategy depends on the system configuration. Simulation results also demonstrate that the proposed adaptive IRS design brings significant R-E enhancement over benchmark schemes for broadband transmission, and the optimal IRS can be approximated in closed form with negligible performance loss for narrowband transmission.
	\end{abstract}
